### 2019-05-24 2-Chapters/2-Chapter/chapter2.tex
C'est un cauchemar je ne sais rien écrire proprement

% - Worst case regret (max $R_T^{r}$ for $r$ index of Monte-Carlo simulation?)
The \emph{switching cost} $SC^{\cA}(T)$ counts how many times the player's decision has changed from one time step to the next one, \ie, $SC^{\cA}(T) = \sum_{t=1}^{T-1} \indic(A(t) \neq A(t+1))$.
It has recently gained interest in the literature, for instance in \cite{Koren17}.
% FIXME give the main result proved in this paper?
In single-player models,
it is easy to show that achieving logarithmic regret directly implies a logarithmic upper-bound on the switching cost, and conversely the lower-bound from \cite{LaiRobbins85} also gives an asymptotic logarithmic lower-bound.
But even if $SC^{\cA}(T) = \Theta(\log T)$ for an efficient algorithm, it can be interesting to numerically evaluate this quantity, as a large value might indicate an algorithm that is alternating too much between the optimal arm and other arms.
%
% FIXME we give notations but I don't use them in Chapter5 
It is more interesting to studying $SC_M^{\cA}(T)$, the sum of the switching costs of the $M$ players in a multi-player bandit game, as in this case, it is possible that the players follow an efficient centralized or decentralized algorithm (which gives a logarithmic centralized regret) while still suffering from a linear switching cost.
It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $SC_M^{\cA}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% - Switching cost? \cite{modiDemo2016} \cite{Koren17}
On a more experimental note, it was showed in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-player bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting means that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for the multi-player case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi}.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret.

@@

% https://smpybandits.github.io/docs/Policies.EpsilonGreedy.html
On the first hand, the $\varepsilon$-greedy strategy, from \cite{SuttonBarto2018}, consists in alternating exploration and exploitation at a certain ratio.
Fix $0<\varepsilon<1$, then at each round, with probability $\varepsilon$ the player selects an arm uniformly at random (exploration) and with probability $1-\varepsilon$ the arm with highest empirical mean is selected (exploitation).
If $\varepsilon$ is constant, then the (mean) regret is still growing linearly as it is lower bounded by $\varepsilon \frac{1}{K} \sum_{k=1}^K \Delta_k T$.
But if we consider $\varepsilon_t$ decreasing with time $t$, for instance $\varepsilon_t = 6 K / (d^2 t)$, for a constant $0 < d < \min_{k: \Delta_k > 0} \Delta_k$,
then it was shown in \cite{Auer02} that the regret is of the order of $K \log(T) / d + \smallO{T}$.

% https://smpybandits.github.io/docs/Policies.ExploreThenCommit.html
On the other hand, the ``explore-then-commit'' strategy, also introduced in \cite{SuttonBarto2018} and studied for instance in \cite{GarivierETC2016}, consists in first exploring uniformly the $K$ arms for $T_0$ time steps, then only exploiting the best arm.
If $T_0$ is fixed independently of $T$ and the problem difficulty, the regret is again growing linearly.

Both strategies give linear regret if they are tuned independently of the problem at hand, but they can be tuned to be efficient (\ie, with logarithmic regret) if lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, they are not applicable on an unknown problem and are less interesting from a practical point-of-view.

@@

@@

@@

@@

It's a good opportunity to show off and say that I worked on my own on some non-standard policies.

>>>>

% - Worst case regret (max $R_T^{r}$ for $r$ index of Monte-Carlo simulation?)
The \emph{switching cost} $SC^{\cA}(T)$ counts how many times the player's decision has changed from one time step to the next one, \ie, $SC^{\cA}(T) = \sum_{t=1}^{T-1} \indic(A(t) \neq A(t+1))$.
It has recently gained interest in the literature, for instance in \cite{Koren17}.
% FIXME give the main result proved in this paper?
In single-player models,
it is easy to show that achieving logarithmic regret directly implies a logarithmic upper-bound on the switching cost, and conversely the lower-bound from \cite{LaiRobbins85} also gives an asymptotic logarithmic lower-bound.
But even if $SC^{\cA}(T) = \Theta(\log T)$ for an efficient algorithm, it can be interesting to numerically evaluate this quantity, as a large value might indicate an algorithm that is alternating too much between the optimal arm and other arms.
%
% FIXME we give notations but I don't use them in Chapter5 
It is more interesting to studying $SC_M^{\cA}(T)$, the sum of the switching costs of the $M$ players in a multi-player bandit game, as in this case, it is possible that the players follow an efficient centralized or decentralized algorithm (which gives a logarithmic centralized regret) while still suffering from a linear switching cost.
It is very satisfying to obtain a logarithmic switching cost for our algorithm \MCTopM-\klUCB{} in Chapter~\ref{chapter:5}, even if minimizing the switching cost was not one of our objective, and the bound we obtain on $SC_M^{\cA}(T)$ is just a consequence of our proof of the control we give on the regret $R^{\cA}(T)$.
% - Switching cost? \cite{modiDemo2016} \cite{Koren17}
On a more experimental note, it was showed in \cite{modiDemo2016} that the previous state-of-the-art policy for multi-player bandits, \rhoRand, could be tuned to run in batches\footnote{~The batch bandit setting means that all players use the same decisions for instance for $50$ consecutive times, and update their decisions only once every $50$ time steps. For more details, see \cite{modiDemo2016} for experiments on the multi-player case, or \cite{perchet2016,gao2019batched,kolnogorov2019multi} for theoretical developments on the single-player case.}, in order to reduce by a certain multiplicative factor its switching cost while only adding an additive factor on its regret.

@@

% https://smpybandits.github.io/docs/Policies.EpsilonGreedy.html
On the first hand, the $\varepsilon$-greedy strategy, from \cite{SuttonBarto2018}, consists in alternating exploration and exploitation at a certain ratio.
Fix $0<\varepsilon<1$, then at each round, with probability $\varepsilon$ the player selects an arm uniformly at random (exploration) and with probability $1-\varepsilon$ the arm with highest empirical mean is selected (exploitation).
If $\varepsilon$ is constant, then the (mean) regret is still growing linearly as it is lower bounded by $\varepsilon \frac{1}{K} \sum_{k=1}^K \Delta_k T$.
But if we consider $\varepsilon_t$ decreasing with time $t$, for instance $\varepsilon_t = 6 K / (d^2 t)$, for a constant $0 < d < \min_{k: \Delta_k > 0} \Delta_k$,
then it was shown in \cite{Auer02} that the regret is of the order of $K \log(T) / d + \smallO{T}$, which leads to an order-optimal regret of $\bigO{\log(T)}$.

% https://smpybandits.github.io/docs/Policies.ExploreThenCommit.html
On the other hand, the ``explore-then-exploit'' strategy, also introduced in \cite{SuttonBarto2018} and studied for instance in \cite{GarivierETC2016}, consists in first exploring uniformly the $K$ arms for $T_0$ time steps, then only exploiting the best arm.
If $T_0$ is fixed independently of $T$ and the problem difficulty, the regret is again growing linearly, as $R_T \geq (\min_{k: \Delta_k > 0} \Delta_k) K T_0 + p (T - T_0)$, if $p$ denotes the probability that the chosen arm is not optimal.
As $p$ only depends on the number of collected samples $T_0$ and not $T$, $R_T = \Omega(T)$.

\begin{proof}
    For the case of two arms,
    for instance, if the distributions are Bernoulli (or sub-Gaussian), we can use Hoeffding's inequality from \cite{hoeffding1963probability} to control this probability $p$.
    %
    Indeed if $Z_1,\dots,Z_n$ are \iid{} samples from a Bernoulli distribution of parameter $\mu$, of mean $\hat{Z}_n$ we have
    \begin{align}
        \forall x < \mu, \bP(\hat{Z}_n) \leq \exp(-2 n (x-\mu)^2),\\
        \forall x > \mu, \bP(\hat{Z}_n) \geq \exp(-2 n (x-\mu)^2).
    \end{align}
    %
    If $\mu_1 = \mu_2 + \Delta$, then
    $p = \bP(\widehat{\mu_1} < \widehat{\mu_2}) \leq \bP(\widehat{\mu_1} < \widehat{\mu_2}) + \bP(\widehat{\mu_1} < \widehat{\mu_2})$, and both terms can be bounded by using Hoeffding's inequality with $n=T_0/2$ samples,
    to obtain $p \leq 2 \exp(-T_0 \Delta^2 / 4)$.
    %
    For $K$ arms, the same proofs applies and we can obtain
    $p \leq 2 K \exp(-T_0 d^2 / 4)$ if $d$ is a lower-bound on the positive gaps.
    %
    It shows that $p$ is a constant wrt $T$.
\end{proof}

Using the same analysis, if a lower-bound $d$ on the positive gaps is known beforehand, one can find a tuning of $T_0$ that gives a logarithmic regret, like for the previous strategy.
%
Like for the lower-bound, we have $R_T \leq (\max_{k: \Delta_k > 0} \Delta_k) K T_0 + p (T - T_0)$, thus $R_T \leq K T_0 + K \exp(-T_0 d^2/4) T$ using Hoeffding's inequality again. Optimizing on $T_0$ gives $T_0 = 4/d^2 \log(d^2 T / 4)$
and $R_T \leq K 4/d^2 (1 + \log(d^2 T / 4)) = \bigO{\log(T)}$.

An extension of the ``exploit-then-exploit'' is to consider not a fixed time $T_0$ but a random time $\tau$ at which exploration stops.
This time $\tau$ must be a \emph{stopping time} in the sense that it is a measurable random variable, dependent of the past observations, as introduced by \cite{Wald45}. The strategy is then referred to as ``explore-then-commit'' (ETC), and the idea is to use a statistical test at every time step $t$, and stop as soon as enough samples were collected to effectively identify the best arm with a certain confidence level $\delta$. Choosing $\delta \propto 1/T$ typically lead to a logarithmic upper-bound on the regret.

For both cases, the strategy obtains a linear regret if it is tuned independently of the problem at hand, but they can be tuned to be efficient (\ie, with logarithmic regret) if lower-bound on the gaps $\Delta_k$ is known.
%  \ie, they require a prior knowledge on the problem difficulty.
As such, they are not applicable on an unknown problem and are less interesting from a practical point-of-view.

@@

% \begin{small} % XXX remove if needed
\begin{figure}[h!]
	\centering
    \begin{framed}
	\begin{algorithm}[H]
		\begin{small} % XXX remove if needed
		\For(){$t = 1, \dots, T$}{
            \uIf{$t \leq K$}{
                Play arm $A(t) = t$\;
            }
			\Else(){
                For each arm, compute the index $U_k(t)$\;
                Play arm $A(t) = \arg\max_{1\leq k \leq K} U_k(t)$\;
            }
            Observe a reward $r_{A(t)}(t)$\;
            Update both $X_k(t)$ and $N_k(t)$\;
		}
		\caption{A generic index policy.}
		\label{algo:2:indexPolicy}
		\end{small} % XXX remove if needed
	\end{algorithm}
	\end{framed}
\end{figure}
% \end{small} % XXX remove if needed

@@

compute the index $U_k(t) = \widehat{\mu_k}(t) + \sqrt{\alpha \log(t) / N_k(t)}$.

@@

compute the index $U_k(t) = XXX$.

@@

It's a good opportunity to show that I worked on my own on some non-standard policies.
